Marzuki Nooranas

### 2023-10-20 index.qmd
Update
update

Such experiences provide me with firsthand insights into how different societies interact, and not only broadening my horizons, but also fostering empathy across different communities. Here's a little snippet!

@@

<p>overland travel for the vibesss. what a way to end 2022 phewww</p>

<a target="_blank" title="♬ original sound - 𝚁𝚊𝚐𝚑𝚊𝚍💗" href="https://www.tiktok.com/music/original-sound-7178872451673459457?refer=embed">♬ original sound - 𝚁𝚊𝚐𝚑𝚊𝚍💗</a>

@@

<a target="_blank" title="♬ moth to a flame x after hours - trlixqy" href="https://www.tiktok.com/music/moth-to-a-flame-x-after-hours-7174186663990561579?refer=embed">♬ moth to a flame x after hours - trlixqy</a>

>>>>

Such experiences provide me with firsthand insights into how different societies interact, and not only broadening my horizons, but also fostering empathy across different communities. Here's a little snippet - My overland journey from Singapore to Vietnam!

@@

<p>overland travel for the vibesss </p>

@@
